---
title: "Family Guy"
author: 
  - Mohammad Saeed Pourjafar^[University of Warsaw, m.pourjafar@student.uw.edu.pl]
date: "30/3/2022"
output: rmdformats::readthedown
---
Loading the usual suspects!
```{r, message=FALSE}
library(dplyr)
library(stringr)
library(rvest)
library(ggplot2)
```


# A brief description
The below paragraph for the <span style="text-decoration: underline">__*Family Guy*__</span> series which created by *Seth MacFarlane*, has been scraped directly from the [Wikipedia](https://en.wikipedia.org/wiki/Family_Guy) page. I hide the source code here for more readability. Please refer to [ASSIGNMENT 2.Rmd](https://github.com/SaeedPourjafar/RRcourse2022/blob/7d8f55fc5417e7a8878b6161db2cfd3b840a249a/RR_Mar_30_31/ASSIGNMENT%202.Rmd) for the source code. Enjoy!

```{r,include=FALSE, cache=TRUE}
desc_url <- "https://en.wikipedia.org/wiki/Family_Guy"

desc <- desc_url %>%
  read_html() %>% 
  html_nodes(xpath='//*[@id="mw-content-text"]/div[1]/p[2]') %>%
  html_text()
  
desc <- substr(desc,T, nchar(desc)-3)
```

>`r desc`

# A SHOT from the show

In case you are curious to meet the Griffin's lovely family, here's a <span style="color: red;">nice SHOT</span> from them.  

```{r, echo=FALSE}
# Define variable containing url
url <- "https://64.media.tumblr.com/a0f6ad5a24c72e407d0668da7eb1bc8a/tumblr_nrl0zrek1E1txi1hfo1_400.gifv"
```

<center><img src="`r url`"></center>

# A summary of some basic statistics

```{r, include=FALSE, cache=TRUE, warning=FALSE}
# The table for rank and viewers
table <- desc_url %>%
  read_html() %>% 
  html_nodes(xpath='//*[@id="mw-content-text"]/div[1]/table[2]/tbody') %>% 
  html_table(fill=TRUE)

# Changing the header names
names(table[[1]]) <- table[[1]][1,]
table <- table[[1]][-1,c(-1,-3)] # Removing the duplicated columns
no_of_seasons <- nrow(table)

# Some calculated vales to use inline text
first_aired <- substr(table$`First aired`[1],T,16)
avg_episode <- round(mean(as.numeric(table$Episodes)))

table <- table %>%
  mutate(`First aired` = 
          gsub("[\\(\\)]", "", 
          regmatches(`First aired`, gregexpr("\\(.*?\\)", `First aired`)))) %>%
  mutate(`Last aired` = 
           gsub("[\\(\\)]", "", 
                regmatches(`Last aired`, gregexpr("\\(.*?\\)", `Last aired`)))) %>%
  mutate(Rank = str_extract(Rank, "[^\\[]+")) %>%
  mutate(`Viewers(in millions)` = str_extract(`Viewers(in millions)`, "[^\\[]+"))

# Changing some data types
table$`Last aired`[20] <- "TBA"
table$`First aired` <- as.Date(table$`First aired`)
table$`Last aired` <- as.Date(table$`Last aired`)
table$`Viewers(in millions)` <- as.numeric(table$`Viewers(in millions)`)
table$Season <- as.numeric(table$Season)
table$Episodes <- as.numeric(table$Episodes)
table$Rank <- as.numeric(table$Rank)
```

For this point, after scraping some data in R which corresponds to [this table](https://en.wikipedia.org/wiki/Family_Guy#Episodes). We found that currently there are **`r no_of_seasons`** seasons aired on FOX network from **`r first_aired`** up until now. The average number of episodes for each season is **`r avg_episode`**. For more details we can see the details in the table below which shows the season, number of episodes, rank, first and last aired date amont the number of viewers in million:

```{r, echo=FALSE, cache=TRUE}
knitr::kable(table)
```

# A graph of the viewership over time

Here's the plot of number of viewers in million per season.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(table, aes(x =`First aired`, y = `Viewers(in millions)`)) +           
  geom_line() + 
  scale_x_date(date_labels = "%Y-%m-%d") + 
  geom_line(color="red", size = 1)+
  geom_point(size=2) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) + 
  scale_x_date(date_labels="%b %Y", breaks = unique(table$`First aired`)) +
  labs(title="Plot of viewers by season",
        x ="Aired date", y = "Viewers in million")
```

# A graph of the season-to-season changes in viewership
```{r, echo=FALSE, cache=TRUE, message=FALSE, fig.dim= c(6,3)}
table <- table %>%
  mutate(diff = `Viewers(in millions)` - lag(`Viewers(in millions)`, default = first(`Viewers(in millions)`)))
```

And here's the plot of of the season-to-season changes in viewership.

```{r, echo=FALSE, message=FALSE, cache=TRUE, warning=FALSE}
ggplot(data=table, aes(x=Season, y=diff)) +
  geom_bar(stat="identity", fill="steelblue")+
  theme_grey() +
  labs(title="Plot of the change of viewers season by season",
       x ="Saeson", y = "Viewers in million")
```

# A short description of the observed changes

```{r, echo=FALSE, cache=TRUE, include=FALSE}
decreased_calculated_number <- abs(round((table$diff[2]/table$`Viewers(in millions)`[1])*100,2))
increased_calculated_number <- round((table$diff[4]/table$`Viewers(in millions)`[3])*100,2)
avg_viewers <- round(mean(table$`Viewers(in millions)`, na.rm = T),2)
```

No shows or series can lasts forever. As we can observe from the plot above, we can immediately recognize the decreased changes of number of viewers through seasons. This change can be seen as a dramatic shift between season 1 and 2 in which the number of viewers has been decreased by **`r decreased_calculated_number`** percent. However the good news is that the after that the show gains some positive feedback which the result can bee seen in the changes from season 3 to season 4 where the number of viewers increased by **`r increased_calculated_number`**. In the end the average number of viewers as of now is **`r avg_viewers`** millions. 

<style>
body {
text-align: justify}
</style>
<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
